Community comparison

### 2019-12-23 code/community.Rmd
minor

# specify factor order, so Chlainomonas always on same side, etc
species_colors <- c("Chlainomonas A"="#984ea3","Chlainomonas rubra"="#984ea3", #purple
                "Sanguina B"="#ff534a", "Sanguina nivaloides"="#ff534a", #red
                # Chloromonas: pastel greens / blues / yellows
                "Chloromonas krienitzii"="#ffa54c","Chloromonas muramotoi C"="#87b1d4", "Chloromonas D"="#94cf92", "Chloromonas F"="#fdfd96", 
                #    orange green                                      pale blu,                   blue green      yellow--only high elev
                "Chloromonas cf. brevispina"="#80c786", "Chloromonas cf. nivalis"="#4aaf86", 
                #                 lt green                            teal
                "Other Chloromonas"="#4aaf53", "Chloromonas"="#4aaf53", 
                # greyish light green
                "Trebouxiophyceae G"="#6a2d2f", "Trebouxiophyceae"="#6a2d2f", # maroon, standout
                "Unknown E"="grey60", "Green cell"="#4aaf53", "Other"="grey60") #greys

@@

stacked_bar +
  theme(legend.position="none")
#18s: check
# cellct: _
# rbcl: _
```

>>>>

# specify factor order, so Chlainomonas always on same side, etc
species_colors <- c("Chlainomonas A"="#ac71b5","Chlainomonas rubra"="#ac71b5", #purple
                "Sanguina B"="#ff534a", "Sanguina nivaloides"="#ff534a", #red
                # Chloromonas: pastel greens / blues / yellows
                "Chloromonas krienitzii"="#ffa54c","Chloromonas muramotoi C"="#87b1d4", "Chloromonas D"="#94cf92", "Chloromonas F"="#fdfd96", 
                #    orange green                                      pale blu,                   blue green      yellow--only high elev
                "Chloromonas cf. brevispina"="#80c786", "Chloromonas cf. nivalis"="#4aaf86", 
                #                 lt green                            teal
                "Other Chloromonas"="#4aaf53", "Chloromonas"="#4aaf53", 
                # greyish light green
                "Trebouxiophyceae G"="#6a2d2f", "Trebouxiophyceae"="#6a2d2f", # maroon, standout
                "Unknown E"="grey60", "Green cell"="#4aaf53", "Other"="grey60") #greys

@@

stacked_bar +
  theme(legend.position="none")
#18s: check
# cellct: _
# rbcl: _
# red green colorblind similatur
```
